\section{Motivation: Coordinate Independence in Physics}

Physical laws must not depend on how we label space.

\subsection*{Why Does This Matter?}

In physics, we describe phenomena using mathematical equations. However, these equations should describe reality itself, not our particular choice of coordinates. Consider:

\begin{itemize}
    \item \textbf{Newton's Laws}: The force on an object doesn't change if you rotate your coordinate system
    \item \textbf{Maxwell's Equations}: Electromagnetic fields behave the same regardless of your reference frame
    \item \textbf{General Relativity}: The curvature of spacetime is independent of coordinate choice
\end{itemize}

This principle is fundamental: \emph{physical reality is invariant, even though our descriptions of it may change with coordinates}.

\subsection*{Example: Velocity}
A particle moving in space has a velocity that exists independently of coordinates.
If we rotate our coordinate axes, the particle does not suddenly move differently — only the \emph{numbers} describing its velocity change.

For instance, a ball moving northward at 5 m/s has the same physical motion whether you describe it in:
\begin{itemize}
    \item Coordinates aligned north-south and east-west
    \item Coordinates rotated 45 degrees
    \item Polar coordinates centered at your location
\end{itemize}

The velocity vector itself (the geometric object) remains the same. Only its components (the numbers in your coordinate system) change.

\subsection*{The Core Distinction}

This distinction between:
\begin{itemize}
    \item the geometric object (velocity)
    \item its coordinate representation (components)
\end{itemize}
is the core motivation for tensors.

\subsection*{Key Principle}
\begin{quote}
If a quantity represents something physical or geometric, then changing coordinates must not change the object itself, only how we describe it.
\end{quote}

Tensors are defined so this principle is automatically satisfied. They provide a mathematical framework where:
\begin{enumerate}
    \item Objects exist independently of coordinates
    \item We can compute how their components transform when we change coordinates
    \item Physical laws written in tensor notation are automatically coordinate-independent
\end{enumerate}

\subsection*{Thought Exercises}

\begin{exercise}
Consider the following physical quantities. For each, identify whether it is coordinate-independent (invariant) or coordinate-dependent:
\begin{enumerate}
    \item The temperature at a point in space
    \item The velocity components $(v_x, v_y, v_z)$ of a moving particle
    \item The speed (magnitude of velocity) of a moving particle
    \item The coordinates $(x, y, z)$ of a point in space
    \item The distance between two points
    \item Newton's second law: $\vec{F} = m\vec{a}$
\end{enumerate}
\textit{Hint: Ask yourself, "If I rotate my coordinate system, does this quantity change?"}
\end{exercise}

\begin{exercise}
Understanding the distinction:
\begin{enumerate}
    \item A car travels east at 60 km/h. You set up coordinates with the x-axis pointing north. What are the velocity components in your coordinate system?
    \item Your friend uses coordinates with the x-axis pointing east. What are the velocity components in their coordinate system?
    \item Did the car's motion change between parts (a) and (b)? What changed?
    \item Explain why we need a mathematical framework that distinguishes between "the velocity" and "the velocity components"
\end{enumerate}
\end{exercise}

\begin{exercise}
Why tensors matter in physics:
\begin{enumerate}
    \item If Maxwell's equations were not coordinate-independent, what would this imply about electromagnetic phenomena?
    \item In general relativity, gravity is described by the curvature of spacetime. Why must this curvature be coordinate-independent?
    \item Give an example of a physical law that would be problematic if it depended on coordinate choice
\end{enumerate}
\end{exercise}

